---
title: "Binomial package"
author: "Jack Tseng"
date: "5-1-19"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial functions
The package '"binomial"' is an elementary implementation of various ways of manipulating binomial variables and creating graphical summaries of that data. 

## using binomial functions
First the user must decide on a trials, probability, and success argument. Then, feeding it into the binomial functions can create a bar graph, or a cumulative line graph displaying possibilities of each scenario (different number of success in given trials) happening. 

## getting started
One way to take the first step is to use bin_choose, which gives the number of different combinations 'k' successes can take place in 'n' trials.

```{r}
#number of ways of getting 7 successes in 10 trials
bin_choose(10,7)
```

## involving probability
Then, we can use bin_probability, which calculates the probability of a specific number of successes happening in a given number of trials and a given probability of success

```{r}
# probability of getting 7 successes in 10 trials with 0.3 probability of success
bin_probability(7,10,0.3)
```

## putting findings into a distribution
Following that, we can calculate the binomial distribution, taking form in a data frame with the 'bindis' and 'data.frame' class. This allows for a more comprehensive view of the specific binomial scenario.

```{r}
bin_distribution(trials = 10, prob = 0.3)
```

## visualizing the distribution in a bar plot
Using a plot function, we can visualize above distribution.

```{r}
dis1 <- bin_distribution(trials = 10, prob = 0.3)
plot(dis1)
```

## Cumulative binomials
There is another functionality in this package, bin_cumulative(), which calculates the cumulative probability of a binomial distribution. The output is a data frame with class 'bincum' and 'data.frame'.

```{r}
bin_cumulative(10,0.3)
```

## visualizing the distribution in a line graph
Using a line graph is more appropriate for cumulative probability, as it can better show direct changes compared to bar graphs.

```{r}
dis2 <- bin_cumulative(10,0.3)
plot(dis2)
```

## Binomial variables
the 'bin_variable' function prints out the parameters of a binomial variable with class 'binvar'. 

```{r}
bin_variable(10,0.3)
```

## Tying everything together
Using the 'summary()' function, we can obtain a summary of the variable, featuring mean, mode, skewness, kurtosis, and variance in a basic format.

```{r}
bin1 <- bin_variable(10,0.3)
summary(bin1)
```

## breakdown of what the other functions do

'bin_mean()' calculates the mean of the binomial distribution

```{r}
bin_mean(10,0.3)
```

'bin_variance()' calculates the varaince of the binomial distribution

```{r}
bin_variance(10,0.3)
```

'bin_mode()' calculates the mode of the binomial distribution

```{r}
bin_mode(10,0.3)
```

'bin_skewness()' calculates the skewness of the binomial distribution
```{r}
bin_skewness(10,0.3)
```

'bin_kurtosis()' calculates the kurtosis of the binomial distribution
```{r}
bin_kurtosis(10,0.3)
```

